### 2017-06-01 04-experimental-setup.tex
Refactor to accomodate the Pascal. Still need strategy graph, ppx line for the Pascal.

Unless indicated otherwise, the experiments described in the next sections
were conducted on the VU~Amsterdam and Leiden DAS5 clusters.  The clusters
consists of 68 and 24 compute nodes respectively. Each node is equipped with
a dual 8-core Intel Xeon E5-2630v3 CPU clocked at 2.40GHz, 64GB of memory and
8TB of storage. The nodes of each site are interconnected by FDR~InfiniBand.
Additionally, the VU cluster is fitted with a number of Nvidia GPUs including
GTX~\mbox{Titan-X/Pascal},
GTX~\mbox{Titan-X/Maxwell}, GTX980, K40c and K20m.

>>>>

Unless indicated otherwise, the experiments described in the next sections
were conducted on the VU~Amsterdam and Leiden DAS5 clusters.  The clusters
consists of 68 and 24 compute nodes respectively. Each node is equipped with
a dual 8-core Intel Xeon E5-2630v3 CPU clocked at 2.40GHz, 64GB of memory and
8TB of storage. The nodes of each site are interconnected by FDR~InfiniBand.
Additionally, the VU cluster is fitted with a number of Nvidia GPUs including
GTX~\mbox{Titan-X(Pascal)},
GTX~\mbox{Titan-X(Maxwell)}, GTX980, K40c and K20m.

### 2017-06-01 gpu-05-03-accelerator.tex
Refactor to accomodate the Pascal. Still need strategy graph, ppx line for the Pascal.

\begin{table}[tb]	% [htb]
  \centering
  \begin{tabular}{l d{2.8} d{2.8}}
    Kernel & Time (seconds) \\
    \hline
    PPX CALC    &  0.0364737 \\
    PPX ACCUM   &  0.083 \\
    SAMPLING    &  0.535599 \\
    UPDATE\_PHI & 25.6598 \\
    UPDATE\_PI  &  0.645875 \\
    THETA SUM   &  0.0483902 \\
    GRADS PAR   &  1.92919 \\
    GRADS SUM   &  9.31122 \\
    UPDATE THETA&  0.0548013 \\
    NORM THETA  &  0.001 \\
    \hline
    TOTAL    & 38.5858 \\
  \end{tabular}
  \caption{Performance break-down of multi-core CPU version without
  vectorization. Model parameters: data set com-DBLP; K=1024, m=4096, n=32.}
  \label{TABLE-CPU}
\end{table}

@@

\begin{table}[tb]	% [htb]
% \center\begin{tabular}{l c c c c c c c c d{3.1}}
% Device & Architecture & cores & Clock & \multicolumn{2}{c}{GFlops} & L2 Cache & Memory & Bandwidth \\ 
%        &              &       & MHz   & single & double            & KB       & GB     & (GB/s) \\ 
% \hline
% K20m        & Tesla   &  2496 &  706        & 3520 & 1170 &      &  5 & 208 \\
% K40c        & Tesla   &  2880 &  745        & 4290 & 1430 &      & 12 & 208 \\
% GTX 980     & Maxwell &  2816 & 1126 (1216) & 4612 &  144 &      &  4 & 336.5 \\
% GTX Titan-X & Maxwell &  3072 & 1000 (1075) & 6144 &  192 & 2048 & 12 & 336.5 \\
%
%
%###########################################################################################
% SPECS FROM:
% http://www.geforce.com/hardware/desktop-gpus/geforce-gtx-titan-x/specifications
% http://www.geforce.com/hardware/desktop-gpus/geforce-gtx-980/specifications
% http://www.nvidia.com/content/PDF/kepler/Tesla-K40-Active-Board-Spec-BD-06949-001_v03.pdf
% http://www.nvidia.com/content/PDF/kepler/Tesla-K20-Active-BD-06499-001-v04.pdf
%
% FLOPS DATA:
% K40: http://international.download.nvidia.com/pdf/kepler/TeslaK80-datasheet.pdf
% K20 & K40: http://www.nvidia.com/content/tesla/pdf/nvidia-tesla-kepler-family-datasheet.pdf
% GTX980 & TITANX: https://en.wikipedia.org/wiki/List_of_Nvidia_graphics_processing_units
\setlength\tabcolsep{0.4em}
\center\begin{tabular}{lc c c c c c}
                         && \multicolumn{5}{c}{Device} \\
\cline{3-7}
              && \multicolumn{2}{c}{GTX Titan-X} & GTX 980 & K40c  & K20m  \\
Specification            && Pascal & Maxwell     &         &       &       \\
\cline{1-1}\cline{3-7}
Number of Cores          && 3584   & 3072        & 2048    & 2880  & 2496  \\
Clock (MHz)              && 1417   & 1000        & 1126    & 745   & 706   \\
GFlops (single)          && 10157  & 6144        & 4612    & 4290  & 3520  \\
GFlops (double)          && 317    & 192         & 144     & 1430  & 1170  \\
Memory (GB)              && 12     & 12          & 4       & 12    & 5     \\
Bandwidth (GB/s)         && 480    & 336.5       & 224     & 288   & 208   \\
\cline{1-1}\cline{3-7}
\\[-1.5ex]
\end{tabular}
\caption{Properties of the GPUs used in the evaluation}
\label{table-gpus}
\end{table}

@@

% TITANX
\begin{figure*}[tb]	% [htb]
  \centering
  \epsfig{file=plots/gpu-sweep-legends.eps, width=1.0\textwidth}
  \setlength\tabcolsep{0em}
  \begin{tabular}{c c c}
  \epsfig{file=plots/titanx-1024-strategies-w1.eps, width=0.33\textwidth} &
  \epsfig{file=plots/titanx-2048-strategies-w1.eps, width=0.33\textwidth} &
  \epsfig{file=plots/k40-1024-strategies-w2.eps, width=0.33\textwidth}
  \end{tabular}
  \caption{Execution time of 1000 \textit{update\_phi} invocations across a sweep of
  	\textit{update\_phi} thread block sizes. The lower figures are a zoom-in into
	the optimal block range of the upper figures.
	Other relevant model parameters: M=4096, n=32.
	% (a) \mbox{Titan-X} GPU, without explicit kernel vectorization;
	% Relevant model parameters: K=1024, M=4096, n=32.
  	% (b) \mbox{Titan-X} GPU, without explicit kernel vectorization;
	% K=2048, M=4096, n=32.
	% (c) K40c GPU, with explicit kernel vectorization of width 2;
	% K=1024, M=4096, n=32.
  }
  % \label{titanx-w1-sweep}
  \label{gpu-sweep}
\end{figure*}

\begin{comment}
% TITANX K=2K
\begin{figure*}[tb]	% [htb]
  \centering
  \epsfig{file=plots/titanx-2048-strategies-w1.eps, width=\textwidth}
  \caption{Execution time of 1000 \textit{update\_phi} invocations using the
  \mbox{Titan-X} GPU,
  without explicit kernel vectorization, across a sweep of
  \textit{update\_phi} thread block
  sizes. Relevant model parameters: K=2048, M=4096, n=32.}
  \label{titanx-w1-sweep-2k}
\end{figure*}
\end{comment}

Figure \ref{gpu-sweep}(a) presents the performance of the GTX~\mbox{Titan-X} GPU
for all 10 strategy flavors, without explicitly vectorizing the kernels. The
x-axis represents different \textit{update\_phi} thread block sizes while the y-axis presents
the total execution time of 1000 invocations of the \textit{update\_phi} kernel. The
naive and shared strategies are labeled NAIVE and SHARED respectively. Further,
each flavor of the code generation strategy is labeled by GEN followed by the 3
choices that identify it.
%
The wide performance range inhibits the readability of the figure,
therefore, a more focused Figure~\ref{gpu-sweep}(a), bottom figure, is provided. As would
be expected, the naive strategy exhibits the worst performance over all
thread block
sizes, as it does not explicitly cache repeated device memory read operations.
The SHARED and \textit{GEN-SSS} strategies come next in terms of performance.
Both strategies cache $Grads_i$, $Probs_i$ and $\pi_i$ in shared memory but
differ in one aspect. Namely, \textit{GEN-SSS} explicitly unrolls the internal
loops of the kernel. However, there is no significant performance difference
between them. The other flavors of the code generation strategy attain higher
performance as they unroll internal loops as well as cache data in
registers. The \mbox{Titan-X} obtains the best performance with the \textit{GEN-RSS}
strategy and a thread block size of 64. The results of explicitly vectorized kernels
are omitted as they obtain worse performance on the \mbox{Titan-X}.

@@

\begin{comment}
% K40
\begin{figure*}[tb]	% [hbt]
  \centering
  \epsfig{file=plots/k40-1024-strategies-w2.eps, width=\textwidth}
  \caption{Execution time of 1000 \textit{update\_phi} invocations using the K40c GPU, with
  explicit kernel vectorization of width 2, across a sweep of
  \textit{update\_phi} thread block
  sizes. Relevant model parameters: K=1024, M=4096, n=32.}
  \label{k40-w2-sweep}
\end{figure*}
\end{comment}

% \looseness=-1
Figure~\ref{gpu-sweep}(c) presents the performance of the K40c GPU
for the same experimental configuration as shown for the \mbox{Titan-X} in
Figure~\ref{gpu-sweep}(a) except that the code
is explicitly vectorized with a vector width of~2. The results
for the other code versions with vector width 4 and no vectorization are
omitted as they exhibit lower performance.
%
Surprisingly, Figure~\ref{gpu-sweep}(c) shows that the NAIVE strategy
outperforms SHARED and some of the GEN strategies. This can be explained by the
unique properties of the Tesla Super Computing line of products to which the
K40c belongs. These GPUs include enhanced L2 caching mechanisms that
accelerate repeated and sparse memory accesses. This is especially advantageous
as it caches repeated reads across streaming multiprocessors. However, the
highest performance is attained by \textit{GEN-RRS} which explicitly employs
registers for both $Probs_i$ and $Grads_i$.

The performance results obtained from the GTX~\mbox{Titan-X} and Tesla~K40c GPUs
reinforce the importance of customizing compute kernels to each GPU's specific
architecture and capabilities. For instance, each GPU achieved its highest
performance by employing a different strategy. Moreover, each GPU displayed
different strategy-performance orderings.

\begin{figure}[tb]	% [htb]
  \centering
  \epsfig{file=plots/gpus.eps, width=0.9\columnwidth}
  \caption{Speedup comparison of best performing parallel configurations of
  each compute device normalized over baseline C++ version. Relevant model
  parameters: K=1024, M=4096, n=32.}
  \label{gpus-fig}
\end{figure}

\begin{figure}[tb]	% [htb]
  \centering
  \epsfig{file=plots/gpu-vector-sweep.eps, width=0.9\columnwidth}
  \caption{Performance of the best performing strategy per GPU, varying the
  vector width, normalized over the non-vectorized kernel. Relevant model
  parameters: K=1024, M=4096, n=32.}
  \label{gpus-v-sweep}
\end{figure}

\subsubsection{Comparison of Compute Devices}
Figure~\ref{gpus-fig} compares the highest speedup achieved by each of the
GTX~\mbox{Titan-X}, GTX980, K40c, K20m and the Intel Xeon CPU relative to the baseline
sequential C++ version. These results are consistent with the relative
capabilities of each device as listed in Table~\ref{table-gpus}. For instance,
the \mbox{Titan-X} achieves the highest speedup of 86 relative to the baseline. At the
other end, the parallel CPU version attains a speedup factor of~20.9.

As vectorization is a popular GPU optimization, it is important to note that
both GTX GPUs achieved their highest performance with non-vectorized kernels.
On the other hand, the Tesla GPUs obtained the best performance with a vector
width of~2. Figure~\ref{gpus-v-sweep} presents the execution time of the best
performing strategy for each of the 4 GPUs. In this figure, the performance is
normalized over the non-vectorized kernel version for each GPU. For instance,
the \mbox{Titan-X} exhibits an overhead factor of approximately 1.8 when using a vector
width of~4. On the other hand, the K40c improves its performance by roughly
20\% when it uses a vector width of~2 compared to the non-vectorized kernel.
Therefore, explicit vectorization of the kernels can be either useful or
harmful depending on the GPU architecture and the specific problem it is
applied to.

>>>>

\begin{table}[tb]	% [htb]
  \centering
  \begin{tabular}{l d{2.8} d{2.8}}
    Kernel & Time (seconds) \\
    \hline
    PPX CALC    &  0.0364737 \\
    PPX ACCUM   &  0.083 \\
    SAMPLING    &  0.535599 \\
    UPDATE\_PHI & 25.6598 \\
    UPDATE\_PI  &  0.645875 \\
    THETA SUM   &  0.0483902 \\
    GRADS PAR   &  1.92919 \\
    GRADS SUM   &  9.31122 \\
    UPDATE THETA&  0.0548013 \\
    NORM THETA  &  0.001 \\
    \hline
    TOTAL    & 38.5858 \\
  \end{tabular}
  \caption{Performance break-down of multi-core CPU version without
  vectorization. Model parameters: data set com-DBLP; K=1024, m=4096, $|\Neighbors|$=32.}
  \label{TABLE-CPU}
\end{table}

@@

\begin{table}[tb]	% [htb]
% \center\begin{tabular}{l c c c c c c c c d{3.1}}
% Device & Architecture & cores & Clock & \multicolumn{2}{c}{GFlops} & L2 Cache & Memory & Bandwidth \\ 
%        &              &       & MHz   & single & double            & KB       & GB     & (GB/s) \\ 
% \hline
% K20m        & Tesla   &  2496 &  706        & 3520 & 1170 &      &  5 & 208 \\
% K40c        & Tesla   &  2880 &  745        & 4290 & 1430 &      & 12 & 208 \\
% GTX 980     & Maxwell &  2816 & 1126 (1216) & 4612 &  144 &      &  4 & 336.5 \\
% GTX Titan-X & Maxwell &  3072 & 1000 (1075) & 6144 &  192 & 2048 & 12 & 336.5 \\
%
%
%###########################################################################################
% SPECS FROM:
% http://www.geforce.com/hardware/desktop-gpus/geforce-gtx-titan-x/specifications
% http://www.geforce.com/hardware/desktop-gpus/geforce-gtx-980/specifications
% http://www.nvidia.com/content/PDF/kepler/Tesla-K40-Active-Board-Spec-BD-06949-001_v03.pdf
% http://www.nvidia.com/content/PDF/kepler/Tesla-K20-Active-BD-06499-001-v04.pdf
%
% FLOPS DATA:
% K40: http://international.download.nvidia.com/pdf/kepler/TeslaK80-datasheet.pdf
% K20 & K40: http://www.nvidia.com/content/tesla/pdf/nvidia-tesla-kepler-family-datasheet.pdf
% GTX980 & TITANX: https://en.wikipedia.org/wiki/List_of_Nvidia_graphics_processing_units
\setlength\tabcolsep{0.4em}
\center\begin{tabular}{lc c c c c c}
                         && \multicolumn{5}{c}{Device} \\
\cline{3-7}
                && \multicolumn{2}{c}{GTX Titan-X} & GTX 980 & K40c  & K20m  \\
Specification            && (Pascal) & (Maxwell)   &         &       &       \\
\cline{1-1}\cline{3-7}
Number of Cores          && 3584     & 3072        & 2048    & 2880  & 2496  \\
Clock (MHz)              && 1417     & 1000        & 1126    & 745   & 706   \\
GFlops (single)          && 10157    & 6144        & 4612    & 4290  & 3520  \\
GFlops (double)          && 317      & 192         & 144     & 1430  & 1170  \\
Memory (GB)              && 12       & 12          & 4       & 12    & 5     \\
Bandwidth (GB/s)         && 480      & 336.5       & 224     & 288   & 208   \\
\cline{1-1}\cline{3-7}
\\[-1.5ex]
\end{tabular}
\caption{Properties of the GPUs used in the evaluation}
\label{table-gpus}
\end{table}

@@

% TITANX
\begin{figure*}[tb]	% [htb]
  \centering
  \epsfig{file=plots/gpu-sweep-legends.eps, width=1.0\textwidth}
  \setlength\tabcolsep{0em}
  \begin{tabular}{c c c}
  \epsfig{file=plots/titanx-1024-strategies-w1.eps, width=0.33\textwidth} &
  \epsfig{file=plots/titanx-2048-strategies-w1.eps, width=0.33\textwidth} &
  \epsfig{file=plots/k40-1024-strategies-w2.eps, width=0.33\textwidth}
  \end{tabular}
  \caption{Execution time of 1000 \textit{update\_phi} invocations across a sweep of
  	\textit{update\_phi} thread block sizes. The lower figures are a zoom-in into
	the optimal block range of the upper figures.
	Other relevant model parameters: M=4096, $|\Neighbors|$=32.
	% (a) \mbox{Titan-X} GPU, without explicit kernel vectorization;
	% Relevant model parameters: K=1024, M=4096, $|\Neighbors|$=32.
  	% (b) \mbox{Titan-X} GPU, without explicit kernel vectorization;
	% K=2048, M=4096, $|\Neighbors|$=32.
	% (c) K40c GPU, with explicit kernel vectorization of width 2;
	% K=1024, M=4096, $|\Neighbors|$=32.
  }
  % \label{titanx-w1-sweep}
  \label{gpu-sweep}
\end{figure*}

\begin{comment}
% TITANX K=2K
\begin{figure*}[tb]	% [htb]
  \centering
  \epsfig{file=plots/titanx-2048-strategies-w1.eps, width=\textwidth}
  \caption{Execution time of 1000 \textit{update\_phi} invocations using the
  \mbox{Titan-X(Maxwell)} GPU,
  without explicit kernel vectorization, across a sweep of
  \textit{update\_phi} thread block
  sizes. Relevant model parameters: K=2048, M=4096, $|\Neighbors|$=32.}
  \label{titanx-w1-sweep-2k}
\end{figure*}
\end{comment}

Figure \ref{gpu-sweep}(a) presents the performance of the Maxwell \mbox{Titan-X} GPU
for all 10 strategy flavors, without explicitly vectorizing the kernels. The
x-axis represents different \textit{update\_phi} thread block sizes while the y-axis presents
the total execution time of 1000 invocations of the \textit{update\_phi} kernel. The
naive and shared strategies are labeled NAIVE and SHARED respectively. Further,
each flavor of the code generation strategy is labeled by GEN followed by the 3
choices that identify it.
%
The wide performance range inhibits the readability of the figure,
therefore, a more focused Figure~\ref{gpu-sweep}(a), bottom figure, is provided. As would
be expected, the naive strategy exhibits the worst performance over all
thread block
sizes, as it does not explicitly cache repeated device memory read operations.
The SHARED and \textit{GEN-SSS} strategies come next in terms of performance.
Both strategies cache $Grads_i$, $Probs_i$ and $\pi_i$ in shared memory but
differ in one aspect. Namely, \textit{GEN-SSS} explicitly unrolls the internal
loops of the kernel. However, there is no significant performance difference
between them. The other flavors of the code generation strategy attain higher
performance as they unroll internal loops as well as cache data in
registers. The Pascal Titan-X is fastest with the \textit{GEN-RSR} strategy and a
block size of 96 and a vector width of~2, whereas
the Maxwell Titan-X obtains the best performance with the \textit{GEN-RSS}
strategy and a thread block size of 64 and no vectorization. The results of other
vector widths
are omitted as they obtain lower performance.

@@

\begin{comment}
% K40
\begin{figure*}[tb]	% [hbt]
  \centering
  \epsfig{file=plots/k40-1024-strategies-w2.eps, width=\textwidth}
  \caption{Execution time of 1000 \textit{update\_phi} invocations using the K40c GPU, with
  explicit kernel vectorization of width 2, across a sweep of
  \textit{update\_phi} thread block
  sizes. Relevant model parameters: K=1024, M=4096, $|\Neighbors|$=32.}
  \label{k40-w2-sweep}
\end{figure*}
\end{comment}

% \looseness=-1
Figure~\ref{gpu-sweep}(c) presents the performance of the K40c GPU
for the same experimental configuration as shown for the Maxwel \mbox{Titan-X} in
Figure~\ref{gpu-sweep}(a) except that the code
is explicitly vectorized with a vector width of~2. The results
for the other code versions with vector width 4 and no vectorization are
omitted as they exhibit lower performance.
%
Surprisingly, Figure~\ref{gpu-sweep}(c) shows that the NAIVE strategy
outperforms SHARED and some of the GEN strategies. This can be explained by the
unique properties of the Tesla Super Computing line of products to which the
K40c belongs. These GPUs include enhanced L2 caching mechanisms that
accelerate repeated and sparse memory accesses. This is especially advantageous
as it caches repeated reads across streaming multiprocessors. However, the
highest performance is attained by \textit{GEN-RRS} which explicitly employs
registers for both $Probs_i$ and $Grads_i$.

The performance results obtained from the Maxwell \mbox{Titan-X} and Tesla~K40c GPUs
reinforce the importance of customizing compute kernels to each GPU's specific
architecture and capabilities. For instance, each GPU achieved its highest
performance by employing a different strategy. Moreover, each GPU displayed
different strategy-performance orderings.

\begin{figure}[tb]	% [htb]
  \centering
  \epsfig{file=plots/gpus.eps, width=0.9\columnwidth}
  \caption{Speedup comparison of best performing parallel configurations of
  each compute device normalized over baseline C++ version. Relevant model
  parameters: K=1024, M=4096, $|\Neighbors|$=32.}
  \label{gpus-fig}
\end{figure}

\begin{figure}[tb]	% [htb]
  \centering
  \epsfig{file=plots/gpu-vector-sweep.eps, width=0.9\columnwidth}
  \caption{Performance of the best performing strategy per GPU, varying the
  vector width, normalized over the non-vectorized kernel. Relevant model
  parameters: K=1024, M=4096, $|\Neighbors|$=32.}
  \label{gpus-v-sweep}
\end{figure}

\subsubsection{Comparison of Compute Devices}
Figure~\ref{gpus-fig} compares the highest speedup achieved by each of the
GTX~\mbox{Titan-X} Maxwell and Pascal, GTX980, K40c, K20m and the Intel Xeon CPU relative to the baseline
sequential C++ version. These results are consistent with the relative
capabilities of each device as listed in Table~\ref{table-gpus}. For instance,
the \mbox{Titan-X(Pascal)} achieves the highest speedup of 120 relative to the baseline. At the
other end, the parallel CPU version attains a speedup factor of~20.9.

As vectorization is a popular GPU optimization, it is important to note that
the Maxwell \mbox{Titan-X} and GTX980 achieve their highest performance with non-vectorized kernels.
On the other hand, the Pascal \mbox{Titan-X} and Tesla GPUs obtain the best performance with a vector
width of~2. Figure~\ref{gpus-v-sweep} presents the execution time of the best
performing strategy for each of the 4 GPUs. In this figure, the performance is
normalized over the non-vectorized kernel version for each GPU. At one extreme,
the Maxwell \mbox{Titan-X} exhibits an overhead factor of nearly 1.8 when using a vector
width of~4. On the other hand, the K40c improves its performance by roughly
20\% when it uses a vector width of~2 compared to the non-vectorized kernel.
Therefore, explicit vectorization of the kernels can be either useful or
harmful depending on the GPU architecture and the specific problem it is
applied to.

### 2017-06-01 gpu-05-05-perplexity.tex
Refactor to accomodate the Pascal. Still need strategy graph, ppx line for the Pascal.

\begin{comment}
\begin{figure}[t]	% [htb]
  \centering
  \epsfig{file=plots/ppx-gpu.eps, width=\columnwidth}
  \caption{Perplexity convergence of com-DBLP on the GTX~\mbox{Titan-X}~GPU. Number
  of communities chosen to maximally fill the GPU memory.}
  \label{fig-ppx-gpu}
\end{figure}

\begin{figure}[t]	% [htb]
  \centering
  \epsfig{file=plots/ppx-cpu.eps, width=\columnwidth}
  \caption{Perplexity convergence of com-LiveJournal on the multi-core~CPU.
  Number of communities chosen to maximally fill the CPU memory.}
  \label{fig-ppx-cpu}
\end{figure}
\end{comment}

\begin{figure}[t]	% [htb]
  \centering
  \epsfig{file=plots/ppx-gpu-cpu.eps, width=0.45\textwidth}
  \caption{Perplexity convergence. (a)~com-DBLP on the GTX~\mbox{Titan-X}~CPU.
  (b)~com-LiveJournal on the multi-core~CPU. Number of communities chosen to
  maximally fill the memory of GPU and CPU respectively.}
  \label{fig-ppx-gpu-cpu}
\end{figure}

@@

Figure~\ref{fig-ppx-gpu-cpu}(a) shows the perplexity development for the dataset
com-DBLP, with $N=317,080$. It is computed on the GTX~\mbox{Titan-X} GPU with input
parameter set $K=4096$, $m=4096$, $n=32$. Convergence is reached after 6~hours.

>>>>

\begin{comment}
\begin{figure}[tb]	% [htb]
  \centering
  \epsfig{file=plots/ppx-gpu.eps, width=\columnwidth}
  \caption{Perplexity convergence of com-DBLP on the Maxwell \mbox{Titan-X}~GPU. Number
  of communities chosen to maximally fill the GPU memory.}
  \label{fig-ppx-gpu}
\end{figure}

\begin{figure}[tb]	% [htb]
  \centering
  \epsfig{file=plots/ppx-cpu.eps, width=\columnwidth}
  \caption{Perplexity convergence of com-LiveJournal on the multi-core~CPU.
  Number of communities chosen to maximally fill the CPU memory.}
  \label{fig-ppx-cpu}
\end{figure}
\end{comment}

\begin{figure}[tb]	% [htb]
  \centering
  \epsfig{file=plots/ppx-gpu-cpu.eps, width=0.45\textwidth}
  \caption{Perplexity convergence. (a)~com-DBLP on the Maxwell \mbox{Titan-X}~GPU.
  (b)~com-LiveJournal on the multi-core~CPU. Number of communities chosen to
  maximally fill the memory of GPU and CPU respectively. M=4K, $|\Neighbors|$=32.}
  \label{fig-ppx-gpu-cpu}
\end{figure}

@@

Figure~\ref{fig-ppx-gpu-cpu}(a) shows the perplexity development for the dataset
com-DBLP, with $N=317,080$. It is computed on the Maxwell \mbox{Titan-X} GPU with input
parameter set $K=4096$, $m=4096$, $n=32$. Convergence is reached after 6~hours.
